Comparing Results with Mafessoni et al.

### 2019-07-04 PlottingScripts/ProcessPlotData.Rmd
updated text and supplementary figures.

>>>>

##Imputation Scores
```{r}
library(data.table)
library(spatstat)
library(rdist)
library(Rfast)
#Imputation scores for Japanese genotyped individuals
suspicious <- fread('/Users/luke/Documents/LegacyData/LatexManuscript/SupplementaryData/Significant_Positions_and_Pvals.txt')
#set path and array name
jpt_imp_path = "/Users/luke/Documents/Legacy_Misc/Misc/ImputationScores/"
array = "610k" #2500k_2500o #ASA #CoreExome24
#list of filenames
jpt_imp_files = list.files(path=jpt_imp_path, 
                           pattern=paste0(array,".imputed.1.info.gz"),
                           full.names = T) 
# Read the files
jpt_imp <- lapply(jpt_imp_files, 
                  function(x) {fread(paste('gzcat', x), 
                                          header = T, 
                                          sep ="\t")})
# Combine them
jpt_imp <- do.call("rbind", 
                   lapply(jpt_imp, as.data.frame))

jpt_imp <- separate(data = jpt_imp, 
                    col = SNP, 
                    into = c("Chr", "Pos"), 
                    sep = ":")

jpt_imp <- merge(jpt_imp, suspicious, 
                 by = c('Chr', 'Pos'), all.x = T)

jpt_imp$Pos <- as.numeric(as.character(jpt_imp$Pos))

jpt_imp
```

```{r}

imputed_position <- jpt_imp$Pos
suspicious_position <- jpt_imp[which(jpt_imp$Adjusted_Log10p > 2),]$Pos

jpt_imp$closest <- unlist(lapply(imputed_position, function(x) suspicious_position[which.min(abs(suspicious_position - x))]))
jpt_imp$dist <- abs(jpt_imp$closest - jpt_imp$Pos)

jpt_imp$dist_2 <- round(jpt_imp$dist, -1)

jpt_imp_sub <- jpt_imp %>%
  select(AvgCall, Rsq, dist_2) %>%
  group_by(dist_2) %>%
  summarise(AvgCall_mean = mean(AvgCall),
            Rsq_mean = mean(Rsq))

#plot distance from nearest suspicious variant 
Rsq <- 
  ggplot(jpt_imp_sub, 
       aes(x= dist_2, 
           y = Rsq_mean)) +
  geom_point() +
  labs(x = "Distance from nearest suspicious variant",
       y = "Rsq") +
  xlim(c(0,10000))

AvgCall <- 
  ggplot(jpt_imp_sub, 
       aes(x= dist_2, 
           y = AvgCall_mean)) +
  geom_point() +
  labs(x = "Distance from nearest suspicious variant",
       y = "Average Call") +
  xlim(c(0,10000))

plot_grid(AvgCall, Rsq, ncol=1)

ggsave(paste0(figurePath,
              "Imputation_Distance_10s.jpg"),
       height = 9,
       width = 9)
```

```{r}

```

### 2019-07-04 PlottingScripts/ProcessedData/ScoopCheck.Rmd
updated text and supplementary figures.

load data
```{r}
t4 <- fread('/Users/luke/Downloads/evy199_supp/TableS4.bed',skip=1)
t5 <- fread('/Users/luke/Downloads/evy199_supp/TableS5.bed',skip=1)
t6 <- fread('/Users/luke/Downloads/evy199_supp/TableS6.bed',skip=1)
t7 <- fread('/Users/luke/Downloads/evy199_supp/TableS7.bed',skip=1)
t8 <- fread('/Users/luke/Downloads/evy199_supp/TableS8.bed',skip=1)

us <- fread('/Users/luke/Documents/LegacyData/LatexManuscript/SupplementaryData/Significant_Positions_and_Pvals.txt')

totalT<- unique(rbind(t4,t5,t6,t7,t8))
totalTus <- merge(us, totalT ,by.x = c('Chr','Pos'),by.y=c('V1','V3'))
totalTusX <- merge(us, totalT ,by.x = c('Chr','Pos'),by.y=c('V1','V3'), all.x=T)
totalTusX[is.na(totalTusX)] <- 1

```{r}
p_comp <- 
  ggplot(totalTusX, 
       aes(x=Adjusted_Log10p, 
           y= -log10(V5))) +
  geom_point(shape = 1) +
  labs(x = 'Q-association',
       y = 'LD-association')

@@

maxFreq <- max(mSNP$Freq)
mSNPplt <- plotContext(mSNP,'Mafessoni')

m_plot <-
  plot_grid(p_comp,
          mSNPplt,
          ncol = 1,
          rel_heights = c(2, 1))

ggsave(paste0(figurePath,
              'Mafessoni_MutSpect.jpg'),
       m_plot, 
       height = 10,
       width = 18)

@@

>>>>

load data
```{r}
#load regression results
Regression <- readRDS('/Users/luke/Documents/Legacy_Misc/Misc/Regression.Rmd')
#load supplementary files from Mafessoni
t4 <- fread('/Users/luke/Downloads/evy199_supp/TableS4.bed',skip=1)

#t5 <- fread('/Users/luke/Downloads/evy199_supp/TableS5.bed',skip=1)

t6 <- fread('/Users/luke/Downloads/evy199_supp/TableS6.bed',skip=1)

#t7 <- fread('/Users/luke/Downloads/evy199_supp/TableS7.bed',skip=1)

#t8 <- fread('/Users/luke/Downloads/evy199_supp/TableS8.bed',skip=1)

#get total unique positions from most conservative tables (i.e cutoff of 1% MAF)
totalT<- unique(rbind(t4,t6))

#totalTus <- merge(Regression, totalT ,by.x = c('Chr','Pos'),by.y=c('V1','V3'))
totalTusX <- merge(Regression, totalT ,by.x = c('Chr','Pos'),by.y=c('V1','V3'), all.x=T)
totalTusX[is.na(totalTusX)] <- 1

totalTusX
```

```{r}
#select rows of interest
#either present in Mafessoni OR significant in our data
library(ggExtra)

to_plot <- totalTusX %>%
           filter(V5 < 1 | Adjusted_Log10p > 2)

p_comp <- 
  ggplot(to_plot, 
       aes(x=Adjusted_Log10p, 
           y= -log10(V5))) +
  geom_point(shape = 1,
             size = 1,
             alpha = 0.3) +
  labs(x = 'Q-association',
       y = 'LD-association') +
  theme_classic() +
  theme(axis.title = element_text(size = 20),
        axis.text = element_text(size = 20))

p_comp <- ggExtra::ggMarginal(p_comp, type = "histogram")

@@

maxFreq <- max(mSNP$Freq)
mSNPplt <- plotContext(mSNP,'LD-associated')

m_plot <-
  plot_grid(p_comp,
          mSNPplt,
          ncol = 1,
          rel_heights = c(4, 1))

ggsave(paste0(figurePath,
              'Mafessoni_MutSpect.jpg'),
       m_plot, 
       height = 12,
       width = 10)

@@

```{r}
#missing in Mafessoni 
m_maf <- to_plot %>%
           filter(V5 == 1 & Adjusted_Log10p > 2)

#missing in ours
m_us <- to_plot %>%
           filter(V5 < 1 & Adjusted_Log10p < 2)

#present in both
both <- to_plot %>%
           filter(V5 < 1 & Adjusted_Log10p > 2)

print(paste("missing in Mafessoni : ",nrow(m_maf), "or : ", nrow(m_maf)/nrow(to_plot)*100) )
print(paste("missing in ours : ",nrow(m_us), "or : ",nrow(m_us)/nrow(to_plot)*100))
print(paste("present in both : ",nrow(both), "or : ",nrow(both)/nrow(to_plot)*100))
print(paste("total : ", nrow(to_plot)))
```
